Rank Comparison

### 2024-07-09 Code/RankComparison.Rmd
added additional tests for dash results

>>>>

Now we test for the men's dash
```{r}
dash <- read.csv("../Data/Clusrank2022vs2023Dash.csv")
colnames(dash) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = dash,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = dash,
                method = "ds",
                exact = TRUE, B = 500000)
```
```{r}
women_dash <- read.csv("../Data/Clusrank2022vs2023WomensDash.csv")
colnames(women_dash) <- c("Time", "Athlete", "Year")
```

```{r}
library(clusrank)
clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_dash,
                method = "ds")

clusWilcox.test(Time, group=Year, cluster = Athlete, data = women_dash,
                method = "ds",
                exact = TRUE, B = 500000)
```
